---
title: "*Who is Better at Sports Video Games*"
output: pdf_document
author: George Abumohor
date: "06/09/2023"
---
##  Sports Video Games Performance

### *Data Collection*

*The data for the performance of participants in sports video games was collected through a series of gaming sessions. Each participant played NBA 2K, Madden, FIFA, and UFC video games. The number of wins and losses were recorded for each game to analyze the performance of the participants.*
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

# Create the dataset
participants <- c("George", "Diego", "Jon", "Carl", "Cisco")
nba2k_wins <- c(8, 6, 10, 7, 5)
nba2k_losses <- c(2, 4, 0, 3, 5)
madden_wins <- c(9, 8, 7, 6, 10)
madden_losses <- c(1, 2, 3, 4, 0)
fifa_wins <- c(7, 8, 6, 9, 5)
fifa_losses <- c(3, 2, 4, 1, 5)
ufc_wins <- c(6, 5, 7, 4, 8)
ufc_losses <- c(4, 5, 3, 6, 2)

# Combine the data into a data frame
game_results <- data.frame(Participant = participants,
                           NBA_2K_Wins = nba2k_wins,
                           NBA_2K_Losses = nba2k_losses,
                           Madden_Wins = madden_wins,
                           Madden_Losses = madden_losses,
                           FIFA_Wins = fifa_wins,
                           FIFA_Losses = fifa_losses,
                           UFC_Wins = ufc_wins,
                           UFC_Losses = ufc_losses)

# Calculate win percentages for each game
game_results_summary <- game_results %>%
  mutate(NBA_2K_Percentage = NBA_2K_Wins / (NBA_2K_Wins + NBA_2K_Losses),
         Madden_Percentage = Madden_Wins / (Madden_Wins + Madden_Losses),
         FIFA_Percentage = FIFA_Wins / (FIFA_Wins + FIFA_Losses),
         UFC_Percentage = UFC_Wins / (UFC_Wins + UFC_Losses)) %>%
  select(-contains("_Wins"), -contains("_Losses"))

```

## Summary of the Dataset


```{r cars}
# Display the summary table
knitr::kable(game_results_summary, caption = "Summary of Sports Video Games Performance", align = "c")
```
# Visualization: Win Percentages



```{r pressure, echo=FALSE}
# Reshape the dataset for visualization
game_results_long <- game_results_summary %>%
  pivot_longer(cols = contains("_Percentage"),
               names_to = "Game",
               values_to = "Win_Percentage") %>%
  mutate(Game = gsub("_Percentage", "", Game))

# Create a colorful conclusive visualization
ggplot(game_results_long, aes(x = Participant, y = Win_Percentage, fill = Game)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title ="Sports Video Games Performance",
       x = "Participant",
       y = "Win Percentage",
       fill = "Game") +
  theme_minimal()


```




*The visualization above displays the win percentages of different participants in sports video games. Each bar represents a participant, and the height of the bar represents their win percentage in a specific game.*

*From the visualization and the summary table, we can conclude that some participants have higher win percentages in certain games compared to others. The dataset provides insights into the performance of each participant in NBA 2K, Madden, FIFA, and UFC video games.*